### 2017-11-08 README.Rmd
Improve documentation and fix image link

## Hypothesis tests
![](figs/ht-diagram.png)

@@

These examples assume that `mtcars` has been overwritten so that the variables
`cyl`, `vs`, `am`, `gear`, and `carb` are `factor`s.

>>>>

## Hypothesis tests

General framework diagram for hypothesis tests in `infer` is [here](https://github.com/andrewpbray/infer/raw/master/figs/ht-diagram.png).

@@

The examples below only show the calculation of randomization-based statistics and assume that `mtcars` has been overwritten so that the variables
`cyl`, `vs`, `am`, `gear`, and `carb` are `factor`s.
